Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-09-10 ThesisJP/Thesis.tex
Added final numbers before printing (ISBN etc.).

~\\
\vspace{10.0cm}
~\\
{\bf NTNU}
\\
Norwegian University of Science and Technology\\
\\
Thesis for the degree of Philosophiae Doctor\\
\\
Faculty of Medicine\\
Department of Circulation and Medical Imaging\\
\\
\copyright\,Jon Petter \AA{}sen\\
\\
ISBN XXX-XX-XXX-XXXX-X (printed version)\\
ISBN XXX-XX-XXX-XXXX-X (electronic version)\\
ISSN XX-XX\\
\\
Doctoral theses at NTNU, 2014:XX\\
\\
Printed by NTNU-trykk

@@

\vspace{0.2cm}
\noindent \emph{Ovennevnte avhandling er funnet verdig til \aa{} forsvares offentlig for graden Philosophiae Doctor (Ph.D.) i medisinsk teknologi. Disputas finner sted ... .}

>>>>

~\\
\vspace{10.0cm}
~\\
{\bf NTNU}
\\
Norwegian University of Science and Technology\\
\\
Thesis for the degree of Philosophiae Doctor\\
\\
Faculty of Medicine\\
Department of Circulation and Medical Imaging\\
\\
\copyright\,Jon Petter Helgesen \AA{}sen\\
\\
ISBN 978-82-326-0448-7 (printed version)\\
ISBN 978-82-326-0449-4 (electronic version)\\
ISSN 1503-8181\\
\\
Doctoral theses at NTNU, 2014:268\\
\\
Printed by NTNU-trykk

@@

\vspace{0.2cm}
\noindent \emph{Ovennevnte avhandling er funnet verdig til \aa{} forsvares offentlig for graden Philosophiae Doctor (Ph.D.) i Medisinsk Teknologi. Disputas finner sted i Auditoriet, Medisinsk teknisk forskningssenter, torsdag 9. oktober 2014 kl. 12.15.}
